\section{Declarations}

\subsection{Ethics approval and consent to participate}

No ethics/consent was required as no patients were recruited for this work, and no individual patient data was used.

\subsection{Consent for publication}

Not applicable.

\subsection{Availability of data and materials}

General model code is available at \url{https://github.com/stroke-modelling/muster2}.

Estimated travel times based on patient and hospital locations is available at \url{https://gitlab.com/michaelallen1966/1811_lsoa_to_acute_hospital_travel/}.

Code for estimation of stroke outcome depending on time to IVT or MT is available at \url{https://github.com/samuel-book/stroke_outcome/}, and is available as a Python package at \url{https://pypi.org/project/stroke-outcome/}.

\subsection*{Competing interests}

GF reports receiving consulting fees from AstraZeneca for management of stroke due to intracerebral haemorrhage (payment to his employer), Bayer for lecture on models of NHS industry working, CSL Behring for stroke trial consultancy, and being Chief Executive of Health Innovation Oxford and Thames Valley which has multiple joint working agreements and medical education grants with industry partners that are contracts with Oxford University Hospitals NHS Trust the host organisation for Health Innovation Oxford and Thames Valley.

\subsection{Authors' contributions}

All authors were involved in the design of the models, and in review/editing of the manuscript.

AL, MA, and KP, coded the models. AL and MA were the primary authors of the paper.


\subsection*{Funding}

This work was funded by National Institute for Health and Care Research (NIHR) Health Services and Delivery Research (Reference NIHR153982). MA was additionally funded by the NIHR Applied Research Collaboration South West Peninsula.

The views expressed in this publication are those of the authors and not necessarily those
of the NIHR or the Department of Health and Social Care.

\subsection*{Acknowledgements}

We thank all participants in co-production workshops which helped to inform the modelling described herein.

